A Toolbox for Manipulating and Assessing Color Palettes for Statistical Graphics

### 2019-03-10 pkg/colorspace/paper/Toolbox/slides.Rnw
typo
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@450 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
incorporate improved influenza images -> also in slides now
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@479 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

@@

\textbf{Emulate:} Color vision deficies.

>>>>

\subsection{Motivation}

\begin{frame}
\frametitle{Motivation}

\vspace*{-0.3cm}

\begin{minipage}{0.54\textwidth}
\only<1,4>{\includegraphics[width=\textwidth]{../../vignettes/screenshots/influenza-rainbow.png}}%
\only<2>{\includegraphics[width=\textwidth]{../../vignettes/screenshots/influenza-rainbow-deutan.png}}%
\only<3>{\includegraphics[width=\textwidth]{../../vignettes/screenshots/influenza-rainbow-gray.png}}%
\only<5>{\includegraphics[width=\textwidth]{../../vignettes/screenshots/influenza-purpleyellow.png}}%
\only<6>{\includegraphics[width=\textwidth]{../../vignettes/screenshots/influenza-purpleyellow-deutan.png}}%
\only<7>{\includegraphics[width=\textwidth]{../../vignettes/screenshots/influenza-purpleyellow-gray.png}}
\end{minipage}
\hspace*{0.6cm}
\begin{minipage}{0.4\textwidth}

\textbf{Map:} Influenza severity in Germany (week 8, 2019).\\

\textbf{Source:} Arbeitsgemeinschaft Influenza, Robert-Koch-Institut.\\

\textbf{Reported in:} SPIEGEL Online, Tagesschau, \dots\\

\visible<2->{\textbf{Problems:} Color vision deficiency.}
\visible<3->{Grayscale.}
\visible<4->{Flashy.\\}

\visible<5->{\textbf{Alternative:} HCL-based sequential palette.}

\end{minipage}

\begin{frame}
\frametitle{Motivation}

\textbf{Need tools for:}
\begin{itemize}
  \item Construction of palettes with better perceptual properties.
  \item Assessment of color palettes.
  \item Manipulation of colors.
\end{itemize}

\pause
\bigskip

\begin{minipage}{0.5\textwidth}
\includegraphics[width=\textwidth]{../../vignettes/screenshots/bobross.jpg}
\end{minipage}
\hspace*{0.6cm}
\begin{minipage}{0.36\textwidth}
\vspace*{-4cm}
Because Bob Ross would not approve of this!
\end{minipage}

@@

\textbf{Emulate:} Color vision deficiencies.
